\LARGE \bf Cascading Situation Assessment for Robots

### 2017-02-24 paper.tex
Update on Overleaf.
Section 'relation to middlewares'

\subsection{Relation to existing robotic middlewares}

@@

\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{l2tor-photo2}
    \caption{A user manipulating objects on RFID mat while an operator monitors the interaction via an {\tt uwds view} client}
    \label{fig|l2torexample}
\end{figure}
\uwds has been used within the European L2TOR project~\cite{L2TOR} to implement

...context + picture

...needs for spatial representation

\subsection*{Architecture}
The scenario consists of a number of \uwds clients that communicate with each other in order to provide an updated virtual representation to the operator. As seen in Figure \ref{fig|l2torexample}, the user interacts with some     
\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{l2tor-timeline}
    \caption{Schema of the \uwds architecture used in L2TOR project pilot study. }
    \label{fig|l2torarchitecture}
\end{figure}
...diagram with the various \uwds clients

>>>>

\subsection*{Relation to existing robotic middlewares}

Like traditional robotic middlewares, \uwds offers a form of distributed
computation based on message passing. However, it distinguishes itself from
existing middleware in several significant ways.

First and foremost, \uwds purposefully does not offer any \emph{general}
capability at distributing computation and data flows amongst independent
components: it focuses specifically on distributing environment models, both
spatial (geometric models) and temporal (events and situations).

While using standard middlewares as \emph{underlying transport} for \uwds would be
technically feasible and relatively easy to implement, it does not offer any
clear advantage over lighter and dedicated message passing libraries like ZeroMQ
or gRPC (the later being the one used by \uwds).

@@

\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{l2tor-photo2}
    \caption{A user manipulating objects on RFID mat while an operator monitors the interaction via an {\tt uwds view} client}
    \label{fig|l2torexample}
\end{figure}
\uwds has been used within the European L2TOR project~\cite{belpaeme2015l2tor} in order to conceptualize and visualize the spatial relations and visibility of the physical objects that users interact with. In one of the scenarios of this project, users are instructed by a NAO robot to manipulate a number of Duplo-like animals on top of a printed background paper. The robot instructions are based on pedagogical strategies to promote spatial relation learning by object manipulation. Such instructions include commands like to place the elephant \textit{on top} or \textit{next to} the cube or put the giraffe \textit{inside} the house.

i will finish this section later today
...needs for spatial representation

\subsection*{Architecture}
The scenario consists of a number of \uwds clients that communicate with each other in order to provide an updated virtual representation to the operator. As seen in Figure \ref{fig|l2torexample}, the user manipulates the physical objects on top of an RFID mat as instructed by the NAO robot.     
\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{l2tor-timeline}
    \caption{Schema of the \uwds architecture used in L2TOR project pilot study. }
    \label{fig|l2torarchitecture}
\end{figure}
...diagram with the various \uwds clients
